%-------------------------
% Resume in Latex
% Author : Manuel de Labra
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


% Set Style
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \vspace{-2pt}\item
     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape Jose Manuel Hernandez de Labra} \\ \vspace{1pt}
    \small +(52) 442-155-6023 $|$ \href{mailto:jmhlabra@gmail.com}{\underline{jmhlabra@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jmhlabra}{\underline{linkedin.com/jmhlabra}} $|$
    \href{https://github.com/Labrapuerta}{\underline{github.com/Labrapuerta}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tecnologico de Monterrey (ITESM)}{Monterrey, NL, Mexico}
      {Bachelor of Science in Biomedical Engineering, Minor in Neuroscience}{Aug. 2018 -- Dec 2023}

%When starting masters
    %\resumeSubheading
      %{Monterrey Institute of Higher Education (ITESM)}{Monterrey, NL, Mexico}
      %{Master of Science in Computer Science}{Aug. 2023 -- Ongoing}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Scientist Intern}{Aug. 2022 -- Dec. 2022}
      {Neuroscience Department, Zambrano Hospital}{Monterrey, NL}
      \resumeItemListStart
        \resumeItem{Cleaned and processed data from various research projects conducted by psychologists and psychiatrists}
        \resumeItem{Developed visual representations of research data, facilitating better understanding of research findings.}
        \resumeItem{Applied machine learning models to classify patients and detect anomalies, enhancing the accuracy of diagnostics}
      \resumeItemListEnd

      
    \resumeSubheading
      {Machine Learning Researcher}{Jan. 2024 -- Present}
      {Core Lab Genomics}{Monterrey, NL}
      \resumeItemListStart
        \resumeItem{Developed and optimized machine learning architectures for the analysis of RNA and biomolecules}
        \resumeItem{Predicted three-dimensional structures of RNA, contributing to a deeper understanding of molecular interactions.}
        \resumeItem{Utilized advanced algorithms to predict docking interactions between biomolecules and proteins, supporting the discovery of potential therapeutic targets and treatments.
}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
    
%-----------PROJECTS-----------
\section{Research Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://2022.igem.wiki/tec-monterrey/index.html}{\textbf{\underline{rnAIR}}} $|$ \emph{Python, Tensorflow, Molecular Biology, Mathematical Modeling}}{Jan. 2022 -- Dec. 2022}
            {\href{https://competition.igem.org/}{\underline{IGEM competition}}} 
          \resumeItemListStart  
            \resumeItem{Developed small RNAs using a neural network to predict binding RNAs that inhibit bacterial gene synthesis, aiming to resensitize bacteria to antibiotics.}
            \resumeItem{Collected and analyzed datasets of small RNAs, conducted extensive research, and successfully developed a model to address antibiotic resistance.}
            \resumeItem{Part of mathematical modeling and programming efforts, ensuring the development of a robust and accurate model}
          \resumeItemListEnd
      \resumeProjectHeading
        {\href{https://app.jogl.io/project/2019?tab=needs}{\textbf{\underline{ADA}}} $|$ \emph{Python, Docker, Tensorflow, Structural Bioinformatics, Molecular Dynamics}}{Jan. 2023 -- Dec. 2023}
        {\href{https://leagues.igem.org/design/2023/seasonfinale}{\underline{IGEM Design League}}} 
          \resumeItemListStart
            \resumeItem{Led the mathematical modeling and programming efforts, driving the development of biosensors for detecting Alzheimer's}
            \resumeItem{Developed aptamers using three-dimensional RNA models that bind to specific proteins}
            \resumeItem{Implemented deep learning architectures, including mesh convolutions, and utilized Azure Virtual Machines for training}
          \resumeItemListEnd
    \resumeProjectHeading
        {\href{https://github.com/Labrapuerta/STRAND}{\textbf{\underline{STRAND}}} $|$ \emph{Python, Azure, Pytorch, Molecular Dynamics}}{Jan. 2024 -- Ongoing}
        {\href{https://tec.mx/es/investigacion}{\underline{Tec de Monterrey Research}}}
          \resumeItemListStart
            \resumeItem{Research on accurately predicting RNA three-dimensional structures, enhancing the understanding of RNA folding and interactions.}
            \resumeItem{Created labeled datasets with precise intramolecular bindings}
            \resumeItem{Utilized graph neural networks to develop more precise secondary structure contact maps}
            \resumeItem{Leveraged contact maps as templates for predicting three-dimensional RNA structures}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Assembler, SQL} \\
     \textbf{Developer Tools}{: Git, Docker, Azure, VS Code, Visual Studio, Conda} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Tensorflow, Pytorch, SkLearn, }
    }}
 \end{itemize}

%-----------Languages-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Spanish}{ - Native} \\
     \textbf{English}{ - C1} \\
     \textbf{French}{ - A1} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
